---
title: 'Data Scientist Interview_MBM: Part-2 '
author: "XiaocuiZhang"
date: "2020/8/1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning=FALSE)
```

```{r results="hide"}
#load librarys and data

library(readxl)
library(dplyr)
library(ggplot2)
library(lubridate)
library(RColorBrewer) 
library(corrgram)
library(visdat)
library(caret)
library(ggfortify)
library(Metrics)
library(Hmisc)
library(relaimpo)
library(car)
library(MLmetrics )

rawdata <- read_excel("data2.xlsx",col_names =T,skip=1,col_types = NULL) 
```

### 1 Data Exploration and Visualization

#### 1.1 Descriptive statistics
```{r}
glimpse(rawdata) 
```

<font color="blue"> 
There are 36 observations of 13 variables in the data set and most the variables are numeric except Month.
</font>

##### 1.2 descriptive statistics 

```{r}
str(rawdata)
summary(rawdata)
```


 * <font color="blue"> Price1 is constant and Price2 and Price3 changed only once during the given period;</br></font>
 * <font color="blue"> Months  are continuous without breakpoints;</br></font> 
 * <font color="blue"> There is a missing value in social(when month=2018/8/1).</font> 

##### 1.3 missing valuses
```{r}
vis_miss(rawdata, cluster = FALSE, sort_miss = FALSE, show_perc = TRUE,
         show_perc_col = TRUE, large_data_size = 9e+05,
         warn_large_data = TRUE)
```

##### 1.4 possible outliers
```{r}
data_num <- scale(rawdata[,-1],center =TRUE, scale = TRUE)
boxplot(x =data_num, use.cols = TRUE, notch = FALSE, varwidth = FALSE,  center=TRUE,
        horizontal = FALSE, col = brewer.pal(n = ncol(data_num), name = "RdBu"),range = 1.5, main = "Boxplots of numerical data")
```


##### 1.5 correlation

```{r warning=FALSE}
corrgram(rawdata[,-1],  
         text.panel = panel.txt,
         main = "Correlation ",
         lower.panel=panel.shade,
         upper.panel=panel.cor)
```

<font color="blue"> Some dimensions(Pirce2&Price3,Radio&TV) are highly correlated(absolute correlation coefficient of >0.7 among two predictors indicates the presence of multicollinearity </font>


##### 1.6 visualziton 
```{r}
library(xts)
temp_sales=xts(rawdata$Sales, rawdata$Month,frequency=12)
plot(temp_sales)
hist(rawdata$Sales)
 

```

<font color="blue"> The sales shows some kind of periodicity and the right-skewed distribution means its mode is larger than mean.</font>


```{r}
ggplot(data = rawdata,aes(y=Sales))+    
  geom_point(data = rawdata,aes(x=Magazine,colour='Magazine'),size=3) +
  geom_point(data = rawdata,aes(x=Newspaper,colour='Newspaper'),size=3)+ 
  geom_point(data = rawdata,aes(x=Radio,colour='Radio'),size=3) +
  geom_point(data = rawdata,aes(x=OOH,colour='OOH'),size=3)+ 
  geom_point(data = rawdata,aes(x=TV,colour='TV'),size=3)+ 
  geom_point(data = rawdata,aes(x=Search,colour='Search'),size=3) +
  geom_point(data = rawdata,aes(x=Display,colour='Display'),size=3) +
  geom_point(data = rawdata,aes(x=Social,colour='Social'),size=3) + xlab ("Media spend")+
  ggtitle ("Sales vs Media spend on different channels ") +
  theme(plot.title = element_text(hjust = 0.5))
```
 
```{r}
X_ad=rawdata[,-c(1,10,11,12,13)]
sales=rawdata$Sales
total_spend=rowSums(X_ad,na.rm=TRUE)
temp=data.frame(sales,total_spend)
ggplot(data = temp,aes(y=sales,x=total_spend))+    
  geom_point(aes(x=total_spend),size=3)+ 
  geom_line(aes(x=total_spend ),size=1)+ geom_smooth(method=lm)+
  xlab("Media spending(all channels)")+ylab("Sales")+
  ggtitle ("sales response to Media spending ") +
  theme(plot.title = element_text(hjust = 0.5))
```


```{r}
Magazine_stock=stats::filter(x=rawdata$Magazine, filter=0.6, method="recursive") 
ggplot(data = rawdata,aes(y=Sales))+    
  geom_point(aes(x=Magazine_stock,colour='Magazine_stock'),size=3)+ 
  geom_line(aes(x=Magazine_stock, colour="Magazine_stock"),size=1)+ 
  geom_point(data =rawdata,aes(x=Magazine,colour='Magazine'),size=3)+
  geom_line(aes(x=Magazine, colour="Magazine"),size=1) +
  xlab("Magazine spending")+ylab("Sales")+
  ggtitle ("The relation between sales and magazine: before or after adstock transformation(rate=0.6)") +
  theme(plot.title = element_text(hjust = 0.6))
```


```{r}
ts_all=ts(rawdata[-1], start = c(2016, 4), freq = 12)
ts_ad=ts(rawdata[,-c(1,10,11,12)], start = c(2016, 4), freq = 12)
ts_price=ts(rawdata[,10:13], start = c(2016, 4), freq = 12)
ts_sales=ts(rawdata$Sales, start = c(2016, 4), freq = 12)

autoplot(ts_ad)+
  ggtitle("Time Series Plot of the media spend") +
  theme(plot.title = element_text(hjust = 0.5))

```

 

### 2 Data preparation

####  2.1 change month's data type  
```{r}
#convert month to datetime
rawdata$Month=as.Date(rawdata$Month, origin="1970-01-01") 
```


####  2.2 impute social 

```{r}
rawdata$Social <- impute(rawdata$Social,0)  #also always 0 on Augest
```

####  2.3 check and transform sales


```{r}
par(mfrow=c(2,2))
acf(ts_sales)
pacf(ts_sales)


acf(log(ts_sales))
pacf(log(ts_sales))
par(mfrow=c(1,1))
```

<font color="blue">The autocorrelation exitsand and log transformation doesn't work.Hence,I try to decompose sales  
to ensure its stationarity and independence</font>

```{r}
ts_sales_components <- decompose(ts_sales) #Sort of a fourier transformation to decompose signal
plot(ts_sales_components, xlab="time (3 years)",cex=5, frame.plot=TRUE,col.axis="grey",col=c("blue"),axes=FALSE)
ts_adjusted_sales <- ts_sales - ts_sales_components$seasonal
plot(ts_adjusted_sales)

acf(ts_adjusted_sales)
pacf(ts_adjusted_sales)
hist(ts_adjusted_sales)

#refrence https://rpubs.com/nihil0/mmm01
```

#### 2.4 train and test split  

* <font color="blue">Observations in the time series are dependent: the past affects the future but the future does not affect;</br></font>
* <font color="blue"> using createTimeSlices(): 24 obervations for training, 6 for validation  and 6 for testing .</font>

```{r}
set.seed(100)
ts_Split<- caret::createTimeSlices(y = 1:36, initialWindow =24, horizon =6, fixedWindow = T,skip = 0)
#horizon: The number of consecutive values in test set sample
# Nested Cross-Validation reference:
# https://lonepatient.top/2018/06/10/time-series-nested-cross-validation.html#2-%E4%BB%BB%E6%84%8F%E9%80%89%E6%8B%A9%E6%B5%8B%E8%AF%95%E9%9B%86  
# https://scikit-learn.org/stable/modules/cross_validation.html
```


### 3 Model traing and tune parameters

```{r}
#seperated datasets  
X_all=rawdata[,-c(1,13)]
X_ad=rawdata[,-c(1,10,11,12,13)]
X_price=rawdata[,10:12]
sales=rawdata$Sales
adjusted_sales=ts_adjusted_sales 

adstock_Rates=seq(from=0, to=1, by=0.05) 
Num_loop=length(ts_Split$train) # how many loops
vali_len=6                      #observation count for valiation

```

##### 3.1 Build  Models and find the proper adstock Rates using Nested Cross-Validation

```{r}
#==================================
# AdstockTransform function
#==================================
#observation: the feature(s) to be transformed
#signal=0 sample linear Adstock transformed;    else: eg signal=1: using complicated method;   more transformation forms could be added.....
#rate : Adstock rate
#==================================
AdstockTransform <- function(observation,rate,signal){
 
  if(signal==0){
    for(i in names(observation))
    {
      observation[[i]]= as.numeric(stats::filter(x=observation[[i]], filter=rate, method="recursive"))
    }
  }
  else{
    for(i in names(observation))
    {
      observation[[i]]= as.numeric(stats::filter(x= 1/(1+exp(-2*observation[[i]])), filter=rate, method="recursive"))
    }
  }
 adstock_Df=data.frame(observation)
 
 return (adstock_Df) 
}
```

```{r}
#==================================
# Get_bestRate function: 
#==================================
# tf_signal：signal=0 sample linear Adstock transformed;    signal=1: using complicated method
# mediaChannel：ad predictors ,like TV, Radio....
# sales：Target variable
# vali_len：how many observations for validation 
# Num_loop：how many times for cv,depends on the observation counts and  createTimeSlices()
# adstock_Rates：a list of Adstock rate 
#==================================

Get_bestRate<-function(tf_signal, mediaChannel,sales,vali_len=6,Num_loop,adstock_Rates){
  
  #Container to save the cv results
  tuningResult<- data.frame(matrix(ncol = 3, nrow = 0))
  colnames(tuningResult) <- c("rate", "R2", "RMSE")
  
  best_Rate=0
  
  for(rate in adstock_Rates)
  {
    for(i in 1:Num_loop)
    {
 
      
      ColNames=names(mediaChannel)
      
      X=data.frame(mediaChannel[ts_Split$train[i][[1]],])
      y=sales[ts_Split$train[i][[1]]]
      nr=nrow(X)
      
      #adstockTransform
      adstock=AdstockTransform(X,rate,tf_signal) 
      #filter first then split Train and Valiation as the first observation in Valiation set should be filtered
      
      
      # training and Valiation  split
      adstock_Train=data.frame(adstock[1:(nr-vali_len),]) 
      adstock_Valia=data.frame(adstock[(nr-vali_len+1):nr,]) 
      
       
      colnames(adstock_Train) <- ColNames
      colnames(adstock_Valia) <- ColNames
      
      
      y_Train=y[1:(nr-vali_len)]
      y_Valia=y[(nr-vali_len+1):nr]
      
 
      
      #Using a multiple regression model to fit the data
      modFit <- lm(y_Train~.,data=adstock_Train)
       
      #Valiation 
      pred_y=predict(modFit,newdata=adstock_Valia)
      
      #meric
      R2=summary(modFit)$r.squared 
      RMSE=rmse(y_Valia,pred_y)
      tuningResult=rbind(tuningResult,data.frame(rate, R2, RMSE) ) 
      
    }
  }
  
  cv_result=tuningResult%>% group_by(rate)%>% 
    summarise(
      R2_avg= mean(R2),
      RMSE_avg = mean(RMSE)
    )
  
  cv_result=data.frame(cv_result) 
  best_Rate=cv_result[which.max(cv_result$R2_avg),1]
  
  out <- list(cv_result=cv_result, best_Rate=best_Rate)
  return(out)
}

```

##### 3.2 supposing all channels have the same adstock_Rate 
```{r warning=FALSE}
#assuming: 
# all the channels have the same adstock_Rates
# Simple Decay-Effect Model 


 result_adjusted=Get_bestRate(0,X_ad,adjusted_sales,vali_len,Num_loop,adstock_Rates) 
 result_adjusted$cv_result
 result_adjusted$best_Rate    #0.00	 0.7397218	
 
 
 #modeling
 ad_adstock_adjusted=AdstockTransform(X_ad,result_adjusted$best_Rate,0)
 modFit.1 <- lm(adjusted_sales~.,data=ad_adstock_adjusted)
 summary(modFit.1)
 
 par(mfrow=c(2,2))
 plot(modFit.1)
 par(mfrow=c(1,1))
 
```


```{r}
#assuming: 
# all the channels have the same adstock_Rates
# complex Decay-Effect Model 

 result_adjusted=Get_bestRate(1,X_ad,adjusted_sales,vali_len,Num_loop,adstock_Rates) 
 result_adjusted$cv_result
 result_adjusted$best_Rate    #0.25  0.7186469
 
 
 #modeling
 ad_adstock_adjusted=AdstockTransform(X_ad,result_adjusted$best_Rate,1)
 modFit.2 <- lm(adjusted_sales~.,data=ad_adstock_adjusted)
 summary(modFit.2)
 
 par(mfrow=c(2,2))
 plot(modFit.1)
 par(mfrow=c(1,1))
```


##### 3.3  supposing each advertising variable has it’s own adstock_Rate

```{r}
#assuming: 
# each advertising variable has it’s own adstock_Rate
# complex Decay-Effect Mode


 # Magazine
 # adjusted_sales
 Magazine=data.frame(X_ad$Magazine)
 result_Magazine=Get_bestRate(1,Magazine,adjusted_sales,vali_len,Num_loop,adstock_Rates) 
 # result_Magazine$cv_result
 # result_Magazine$best_Rate   #0.75
 
 
 # Newspaper
 # adjusted_sales
 Newspaper=data.frame(X_ad$Newspaper)
 result_Newspaper=Get_bestRate(1,Newspaper,adjusted_sales,vali_len,Num_loop,adstock_Rates) 
 # result_Newspaper$cv_result
 # result_Newspaper$best_Rate   #0.75
 

 
 # Radio
 # adjusted_sales
 Radio=data.frame(X_ad$Radio)
 result_Radio=Get_bestRate(1,Radio,adjusted_sales,vali_len,Num_loop,adstock_Rates) 
 # result_Radio$cv_result
 # result_Radio$best_Rate   # 0.90 
 
 
 # OOH
 # adjusted_sales
 OOH=data.frame(X_ad$OOH)
 result_OOH=Get_bestRate(1,OOH,adjusted_sales,vali_len,Num_loop,adstock_Rates) 
 # result_OOH$cv_result
 # result_OOH$best_Rate   #  0.80 
 
 
 # TV
 # adjusted_sales
 TV=data.frame(X_ad$TV)
 result_TV=Get_bestRate(1,TV,adjusted_sales,vali_len,Num_loop,adstock_Rates) 
 # result_TV$cv_result
 # result_TV$best_Rate   # 0.40  
  
 
 # Search
 # adjusted_sales
 Search=data.frame(X_ad$Search)
 result_Search=Get_bestRate(1,Search,adjusted_sales,vali_len,Num_loop,adstock_Rates) 
 # result_Search$cv_result
 # result_Search$best_Rate   # 0.2 
 
 
 
 # Display
 # adjusted_sales
 Display=data.frame(X_ad$Display)
 result_Display=Get_bestRate(1,Display,adjusted_sales,vali_len,Num_loop,adstock_Rates) 
 # result_Display$cv_result
 # result_Display$best_Rate   # 0.2 
 
 
 # Social
 # adjusted_sales
 Social=data.frame(X_ad$Social)
 result_Social=Get_bestRate(1,Social,adjusted_sales,vali_len,Num_loop,adstock_Rates) 
 # result_Social$cv_result
 # result_Social$best_Rate   # 0.4 
 
 #"Magazine"  "Newspaper" "Radio"     "OOH"       "TV"        "Search"    "Display"   "Social"    
Magazine.adstock=AdstockTransform(Magazine,result_Magazine$best_Rate,1)
Newspaper.adstock=AdstockTransform(Newspaper,result_Newspaper$best_Rate,1)
Radio.adstock=AdstockTransform(Radio,result_Radio$best_Rate,1)
OOH.adstock=AdstockTransform(OOH,result_OOH$best_Rate,1)
TV.adstock=AdstockTransform(TV,result_TV$best_Rate,1)
Search.adstock=AdstockTransform(Search,result_Search$best_Rate,1)
Display.adstock=AdstockTransform(Display,result_Display$best_Rate,1)
Social.adstock=AdstockTransform(Social,result_Social$best_Rate,1)
 
#modeling
media_ad=c(Magazine.adstock,Newspaper.adstock,Radio.adstock,OOH.adstock,TV.adstock,Search.adstock,Display.adstock,Social.adstock)
modFit.3 <-lm(adjusted_sales~.,data=media_ad)
summary(modFit.3)
 
par(mfrow=c(2,2))
plot(modFit.3)
par(mfrow=c(1,1))
```
```{r}
ChannelName=names(X_ad)
AdstockRate=c(result_Magazine$best_Rate, 
              result_Newspaper$best_Rate,
              result_Radio$best_Rate,
              result_OOH$best_Rate,
              result_TV$best_Rate,
              result_Search$best_Rate ,
              result_Display$best_Rate,
              result_Social$best_Rate)
cbind(ChannelName,AdstockRate)
```

```{r}
#assuming: 
# each advertising variable has it’s own adstock_Rate
# simple  Decay-Effect Mode

# Magazine
# adjusted_sales
Magazine=data.frame(X_ad$Magazine)
result_Magazine=Get_bestRate(0,Magazine,adjusted_sales,vali_len,Num_loop,adstock_Rates) 
# result_Magazine$cv_result
# result_Magazine$best_Rate    #0.6

# Newspaper
# adjusted_sales
Newspaper=data.frame(X_ad$Newspaper)
result_Newspaper=Get_bestRate(0,Newspaper,adjusted_sales,vali_len,Num_loop,adstock_Rates) 
# result_Newspaper$cv_result
# result_Newspaper$best_Rate   #1

# Radio
# adjusted_sales
Radio=data.frame(X_ad$Radio)
result_Radio=Get_bestRate(0,Radio,adjusted_sales,vali_len,Num_loop,adstock_Rates) 
# result_Radio$cv_result
# result_Radio$best_Rate   #0

# OOH
# adjusted_sales
OOH=data.frame(X_ad$OOH)
result_OOH=Get_bestRate(0,OOH,adjusted_sales,vali_len,Num_loop,adstock_Rates) 
# result_OOH$cv_result
# result_OOH$best_Rate    #1

# TV
# adjusted_sales
TV=data.frame(X_ad$TV)
result_TV=Get_bestRate(0,TV,adjusted_sales,vali_len,Num_loop,adstock_Rates) 
# result_TV$cv_result
# result_TV$best_Rate   #0


# Search
# adjusted_sales
Search=data.frame(X_ad$Search)
result_Search=Get_bestRate(0,Search,adjusted_sales,vali_len,Num_loop,adstock_Rates) 
# result_Search$cv_result
# result_Search$best_Rate    #0.6

# Display
# adjusted_sales
Display=data.frame(X_ad$Display)
result_Display=Get_bestRate(0,Display,adjusted_sales,vali_len,Num_loop,adstock_Rates) 
# result_Display$cv_result
# result_Display$best_Rate  #0

# Social
# adjusted_sales
Social=data.frame(X_ad$Social)
result_Social=Get_bestRate(0,Social,adjusted_sales,vali_len,Num_loop,adstock_Rates) 
# result_Social$cv_result
# result_Social$best_Rate   #0.35

#"Magazine"  "Newspaper" "Radio"     "OOH"       "TV"        "Search"    "Display"   "Social"    
Magazine.adstock=AdstockTransform(Magazine,result_Magazine$best_Rate,0)
Newspaper.adstock=AdstockTransform(Newspaper,result_Newspaper$best_Rate,0)
Radio.adstock=AdstockTransform(Radio,result_Radio$best_Rate,0)
OOH.adstock=AdstockTransform(OOH,result_OOH$best_Rate,0)
TV.adstock=AdstockTransform(TV,result_TV$best_Rate,0)
Search.adstock=AdstockTransform(Search,result_Search$best_Rate,0)
Display.adstock=AdstockTransform(Display,result_Display$best_Rate,0)
Social.adstock=AdstockTransform(Social,result_Social$best_Rate,0)

#modeling
media_ad=c(Magazine.adstock,Newspaper.adstock,Radio.adstock,OOH.adstock,TV.adstock,Search.adstock,Display.adstock,Social.adstock)
modFit.4 <-lm(adjusted_sales~.,data=media_ad)
summary(modFit.4)

par(mfrow=c(2,2))
plot(modFit.4)
par(mfrow=c(1,1))


```

<font color="blue">
 modFit.4 has the larger R2  among the models ,so 60.36% of the variability of the response data can bee explained by the model.
</font>

```{r}
##Checking for multicolinearity within the independent variables using VIF 
vif(modFit.4) 
```

<font color="blue">
Most scores are less than 5 except OOH,but it still leee than 10, so we could assume there is no multicolliniarity between the independent variables.
</font>

```{r}
##----compare  
modFit.0 <-lm(sales~.,data=X_ad)
modFit.0_1 <-lm(adjusted_sales~.,data=X_ad)
R2_before_0=summary(modFit.0)$r.squared 
R2_before=summary(modFit.0_1)$r.squared
R2_after=summary(modFit.4)$r.square
R2_before_0
R2_before
R2_after 
```

<font color="blue"> Model performence increases when adstock is involved. </font>


#### 3.4 Model reuslts analysis


#####  3.4.1 Adstock rate 
```{r}
#Adstock rate is a measurement of the advertising decay effect.  
ChannelName=names(X_ad)
AdstockRate=c(result_Magazine$best_Rate, 
        result_Newspaper$best_Rate,
        result_Radio$best_Rate,
        result_OOH$best_Rate,
        result_TV$best_Rate,
        result_Search$best_Rate ,
        result_Display$best_Rate,
        result_Social$best_Rate)
cbind(ChannelName,AdstockRate)
```


#####  3.4.2 Decay effect 

Adstock Affect: the prolonged or lagged effect of advertising on consumer purchase behaviour</br>
There are two dimensions to advertising adstock:</br>
*  Decay effect:the impact of past advertisement on present sales;</br>
*  saturation or diminishing returns effect.</br>

<font color="blue"> According to the Adstock Rates we have got in this case, decay effect exits on Magazine,Newspaper,OOH,Search and Social channels.</font>

Take the magezine as an example,

```{r}
Magazine.adstock=AdstockTransform(Magazine,0.6,0)
Magazine.adstock=data.frame(Magazine.adstock[[1]])
colnames(Magazine.adstock)="Magazine.adstock"
Magazine.original=rawdata$Magazine
Sales=rawdata$Sales
#adjusted_sales
compare_df=data.frame(Sales,adjusted_sales,Magazine.original=Magazine.original,Magazine.adstock=Magazine.adstock)
```
 
```{r}
mg_lm_1=lm(adjusted_sales~Magazine.original,data=compare_df)
mg_lm_2=lm(adjusted_sales~Magazine.adstock,data=compare_df)

intercept1=coefficients(summary(mg_lm_1))[1] 
slope1=coefficients(summary(mg_lm_1))[2]
R2_1=summary(mg_lm_1)$r.squared

intercept2=coefficients(summary(mg_lm_2))[1] 
slope2=coefficients(summary(mg_lm_2))[2]
R2_2=summary(mg_lm_2)$r.squared

```

```{r}
Before_Adstock=c(intercept1,slope1,R2_1)
Aftter_Adstock=c(intercept2,slope2,R2_2)
result_comp=rbind(Before_Adstock,Aftter_Adstock)
colnames(result_comp)<-c("Intercept","Slope","R2")
result_comp
```
 
 
```{r}
ggplot(data =compare_df,aes(y=Sales,x=Magazine.original))+    
  geom_point(data =compare_df,aes(x=Magazine.original,colour='red'),size=3)+
  geom_line(aes(x=Magazine.original, colour="red"),size=1) +
  xlab("Magazine spending")+ylab("Sales")+
  ggtitle ("Sales vs. Magazine Before Adstock") +geom_smooth(method=lm)+
  theme(plot.title = element_text(hjust = 0.5))
```
 
```{r}
ggplot(data = compare_df,aes(y=Sales,x=Magazine.original))+    
  geom_point(data =compare_df,aes(x=Magazine.adstock,colour='blue'),size=3)+
  geom_line(aes(x=Magazine.adstock, colour="blue"),size=1) +
  xlab("Magazine spending")+ylab("Sales")+
  ggtitle ("Sales vs. Magazine After Adstock") +geom_smooth(method=lm)+
  theme(plot.title = element_text(hjust = 0.5))
 
```


```{r}
#How much to spend on marketing activities to increase sales by some percent (15%)?
summary(modFit.4)
```

* <font color="blue"> The base sales(adjusted) is 1546;</font>
* <font color="blue"> For one  unit increase in Radio spending, there  will be a 0.011 unit  increase in adjusted_sales;</font>
* <font color="blue"> ??? Why negtive slopes?</font>
 

### 4 Model  testing

```{r warning=FALSE}
#all the ad_transformed media spend 
media_ad=data.frame(media_ad)  #got when buiding modFit.4
adjusted_sales

#ts_Split$train
#ts_Split$test
 
ColNames=names(media_ad)

testing_result<- data.frame(matrix(ncol = 3, nrow = 0))
colnames(testing_result) <- c( "R2", "RMSE","MAPE")

for(i in 1:Num_loop)
{
  #get the trainnin and testing data 
  adstock_Train=data.frame(media_ad[ts_Split$train[i][[1]],])
  y_Train=adjusted_sales[ts_Split$train[i][[1]]]
  
 
  adstock_Test=data.frame(media_ad[ts_Split$test[i][[1]],])
  y_test=adjusted_sales[ts_Split$test[i][[1]]]
 
  colnames(adstock_Train) <- ColNames
  colnames(adstock_Test) <- ColNames
  
  modFit <-lm(y_Train~.,data= adstock_Train)
  
  
  #test 
  y_pred=predict(modFit,newdata=adstock_Test)
  
  #meric
  R2=summary(modFit)$r.squared 
  RMSE=rmse(y_test,y_pred) # rmse(actual, predicted)
  MAPE=MAPE(y_pred,y_test)# MAPE(y_pred, y_true)
  testing_result=rbind(testing_result,data.frame(R2, RMSE,MAPE) ) 
  
} 
 
testing_result%>%  
  summarise(
    R2_avg= mean(R2),
    RMSE_avg = mean(RMSE),
    MAPE_avg = mean(MAPE)
)
```

<font color="blue"> Model having MAPE nearly  10% is considered as not bad model.</font>




### 5 Contribution Charts 
```{r warning=FALSE}
# calculating the relative importance of different marketing variables and structural components
 
relative_importance=calc.relimp(modFit.4, type = c("car"), rela = TRUE)
#used 'car' as cost function; rela=TRUE give % that a variable contributed to the adjusted R2
relative_importance
relative_imp=relative_importance$car


contribution=data.frame(cbind(ChannelName=ChannelName,relative_imp=as.character(relative_imp)))%>%arrange(desc(relative_imp))  
contribution$relative_imp=as.numeric(as.character(contribution$relative_imp))
 
ggplot(data = contribution, mapping = aes(x = reorder(ChannelName, round(contribution$relative_imp,3)), y = relative_imp,fill='steelblue'))+ 
  geom_bar(stat = 'identity')+ 
    xlab ("Media Channel")+
    ylab("Relative Importance") +
    ggtitle ("Drivers of sales")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=F)+coord_flip()  

summary(modFit.4)
```
```{r}

#what is the unit of sales? 
# adjusted_sales?

sales_sum=sum(rawdata$Sales)
revenue_of_each_variable=relative_imp*sales_sum
spending_of_each_variable=colSums(X_ad) 
ROAS=revenue_of_each_variable/spending_of_each_variable
ROAS


print("====================")
sales_sum_1=sum(rawdata$Sales*(rawdata$Price1+rawdata$Price2+rawdata$Price3))
revenue_of_each_variable_1=relative_imp*sales_sum_1
ROAS_1=revenue_of_each_variable_1/spending_of_each_variable

ROAS_1
 
```
 
 

### 6 The following steps

* <font color="blue"> considering the prices;</br> </font>
* <font color="blue"> feature selection; </br> </font>
* <font color="blue"> model Selection;</br> </font>
* <font color="blue"> any other optimization;</br> </font>
* <font color="blue"> is the ROAS right?</br> </font>

 

#### 7 Reference
* https://www.listendata.com/2019/09/marketing-mix-modeling.html
* https://lonepatient.top/2018/06/10/time-series-nested-cross-validation.html#2-%E4%BB%BB%E6%84%8F%E9%80%89%E6%8B%A9%E6%B5%8B%E8%AF%95%E9%9B%86  
* https://scikit-learn.org/stable/modules/cross_validation.html
* https://github.com/shatrunjai/MarketMixModelling/blob/master/FinalCode.R
* https://rpubs.com/nihil0/mmm01
* https://mpra.ub.uni-muenchen.de/7683/4/MPRA_paper_7683.pdf
* https://www.dataapplab.com/towardsdatascience-com-market-mix-modeling/
* https://www.latentview.com/marketing-mix-modeling/
* https://en.wikipedia.org/wiki/Advertising_adstock

